\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\usepackage{multicol}                % enable multiple columns
\raggedright                         % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% PDF metadata / ATS keywords
\hypersetup{
  pdfauthor={Ryan Heyser},
  pdftitle={Ryan Heyser — Resume},
  pdfkeywords={SRE, SLO, SLI, error budget, incident response, runbooks, OpenTelemetry, tracing, Terratest, Packer, canary deployments, blue-green, feature flags, chaos engineering, Istio, Linkerd, Kafka, MinIO, FinOps, Golang, Terraform, Kubernetes, GCP, Vault}
}

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2.5pt, leftmargin=8pt, topsep=6.5pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Ryan Heyser}

\vspace{5pt}

% contact information
\centerline{\href{mailto:ryan.heyser@gmail.com}{ryan.heyser@gmail.com} | \href{https://github.com/ryanheyser}{github.com/ryanheyser}}

\vspace{-18.5pt}

% profile section
\section*{Profile}
\begin{description}
\item\textbf{Technical leader with 10+ years building and operating scalable cloud platforms (GCP, Kubernetes, Terraform).} Experienced leading cross-functional platform teams, defining technical strategy and roadmaps, and driving reliability and operational excellence through SRE practices. Proven ability to hire and mentor engineers, align engineering initiatives with business objectives, and deliver measurable improvements in onboarding, cost optimization, and uptime.\\
\end{description}

\vspace{-18.5pt}

% Leadership & People section (manager-focused)
\section*{Leadership \& People}
\begin{description}
\begin{multicols}{2}
\item\textbf{Coaching \& Career Dev:} Ran mentorship programs and regular 1:1s to improve retention and performance.
\vspace{-8.5pt}
\item\textbf{Communication:} Presented to executives and cross-functional teams; facilitated decision-making.
\vspace{-8.5pt}
\item\textbf{Delivery \& Strategy:} Set OKRs, owned roadmaps, drove prioritization and trade-offs.
\vspace{-8.5pt}
\item\textbf{FinOps \& Budgeting:} Analyzed platform for cost-optimizations.
\columnbreak
\item\textbf{Hiring \& Onboarding:} Designed interview pipelines and onboarding programs reducing ramp time.
\vspace{-8.5pt}
\item\textbf{Stakeholder Management:} Aligned roadmap with product and executive priorities; managed cross-organizational initiatives.
\vspace{-8.5pt}
\item\textbf{Team Leadership:} Built and scaled platform teams; mentoring, peer-level performance reviews.
\vspace{-8.5pt}
\item\textbf{Technical (summary):} GCP, Kubernetes, Terraform — technical credibility to lead cloud platform teams.
\end{multicols}
\end{description}

\vspace{-18.5pt}
% education section
\section*{Education}
\begin{description}
\item\textbf{Florida Atlantic University} -- MS in Computer Engineering \hfill August 2013
\vspace{-9.5pt}
\item\textbf{Georgia Institute of Technology} -- BS in Computer Engineering \hfill August 2011
\end{description}

\vspace{-18.5pt}

\section*{Experience}
\begin{description}
\item\textbf{Staff Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill March 2024 -- Present \\
\textbf{Team:} Cloud Platform Engineering \\
\textit{Lead Platform Engineer position focused on both software development of platform APIs and platform management. Position includes a 24x7 on-call shift. Provide high-level customer support as the Hashicorp Vault platform subject matter expert. Support Google Cloud Infrastructure via terraform enterprise and sentinel policy-as-code.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Implemented custom DERP servers for cloud-wide Tailscale tailnet communication. Maintain 99.999\% uptime.
  \item \textbf{Application:} Developed Github Actions to automate building of operating system and container images.
  \item \textbf{Deliverability:} Integrated AI-assisted automation (Gemini, MCP server) into release pipelines to generate documentation and select targeted tests, improving release deliverability and reducing manual effort.
  \item \textbf{Development:} Implemented terraform providers and observability tooling in Golang to streamline provisioning and monitoring.
  \item \textbf{Documentation:} Designed and implemented standardized documentation templating engine via Confluence. Increased documentation creation by the team by over 1000\% the previous two quarters.
  \item \textbf{FinOps:} Led targeted monitoring cost reductions and retention tuning to reduce recurring platform spend.
  \item \textbf{Incident Management:} Built incident response runbooks, on-call rotation, and blameless postmortem practices, reducing MTTR significantly.
  \item \textbf{Leadership:} Owned platform roadmap and led cross-team stakeholder alignment; led hiring, mentorship, and retention initiatives to improve ramp and performance.
  \item \textbf{Leadership:} Ran people-development programs (weekly "lesson of the week") and maintained an open-door 1:1 practice.
  \item \textbf{Leadership:} Home Depot Infrastructure LEAD Program Graduate.
  \item \textbf{Metrics:} Designed and implemented smoke testing infrastructure for Terraform Enterprise implementation. Increased observability of Terraform Enterprise platform and identified cause of systemic deployment issues affecting customers.
  \item \textbf{Reliability:} Maintained 0 Low/Medium/High/Critical CVEs for 2H 2024.
  \item \textbf{Reliability:} Defined SLO/SLI targets and error-budget processes for platform services, improving availability and customer reliability.
  \item \textbf{Reliability:} Added canary rollouts, automated rollback gates, and deployment verification to CI/CD, cutting failed production deploys.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Staff Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill May 2021 -- March 2024 \\
\textbf{Team:} Developer Operations and Platform Engineering \\
\textit{Lead Platform Engineer position focused on both software development of platform APIs and platform management. Position includes a 24x7 on-call shift. Designed and implemented Kubernetes in the datacenter. Provide high-level customer support as the Kubernetes platform subject matter expert. Provide L4 support for the prior application platform, VMware Tanzu.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Developed a terraform process to create Kubernetes clusters. Process improved Kubernetes customer cluster onboarding down from 2 business weeks to 15 minutes.
  \item \textbf{Application:} Developed Github Actions to automate building of operating system and container images.
  \item \textbf{Leadership:} Designed and ran team mentorship and people-development programs, and maintained an open-door 1:1 practice to improve shared knowledge and ramp.
  \item \textbf{Metrics:} Designed and implemented metrics and logging infrastructure for Kubernetes to egress metrics and logs from datacenter to Google Cloud.
  \item \textbf{Reliability:} Developed node exporter providing additional metrics of Kubernetes node information in Prometheus format in Golang.
  \item \textbf{Reliability:} Developed node smoke test application to provide real-time cluster status information in Golang.
  \item \textbf{Reliability:} Analyzed metrics usage and was able to reduce recurring cost by half.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Senior Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill October 2019 -- May 2021 \\
\textbf{Team:} Developer Operations and Platform Engineering \\
\textit{Senior Systems Engineer position focused on both platform management. Position includes a 24x7 on-call shift. Provide high-level customer support. Develop standard template for documentation to improve developer experience with increased ability to document team and external documentation.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Worked to migrate 1000+ applications on VMware Tanzu from CFLINUXFS2 to CFLINUXFS3 over a 3-day period.
  \item \textbf{Documentation:} Created documentation to assist both team standard operating procedure and customers for VMware Tanzu.
  \item \textbf{Reliability:} Maintain supported and secure VMware Tanzu through multiple upgrades.
  \item \textbf{Reliability:} Bring stability to the VMware Tanzu by integrating Min.io, an S3 data backend, significantly reducing customer impact during maintenance windows. 
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Verification Engineer:} {Telchemy} -- Duluth, GA \hfill April 2015 -- October 2019 \\
\textit{Designed and implemented automated test tool framework to improve validation of software. Provided high level customer support as an interface between the customer and the development team. Designed and maintained secure lab network providing test framework for 100+ devices and 5000+ virtual devices. Provided manual analysis of reports to validate software stack.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Built, tested, documented and maintained software regression testing tool suite reducing testing cycle from months to weeks. 
  \item \textbf{Documentation:} Produce method of procedure maintenance guidelines, produce recommended security practices documentation, for customer integration of products.
  \item \textbf{Reliability:} Designed complex networking configuration for lab testing environment, including network monitoring of all traffic for analysis.
  \item \textbf{Reliability:} Maintain thousands of Linux container instances (LXC, docker) in datacenter.
  \item \textbf{Reliability:} Maintain hundreds of virtual machines (KVM/QEMU, VirtualBox, VMware).
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Airman First Class:} {United States Air Force} -- Boca Raton, FL, Montgomery, AL \hfill October 2012 -- January 2014 \\
\textit{Enrolled in the Technical Degree Sponsorship Program with the US Air Force as an Airman First Class to complete required service.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Documentation:} Compiled and wrote documentation of program development and subsequent revisions, inserting comments in the coded instructions so others could understand the program.
  \item \textbf{Application:} Built, tested, and/or modified prototypes using workflow models or theoretical models constructed with computer simulation.
  \item \textbf{Application:} Prepared detailed workflow charts and diagrams that described input, output, and logical operation and converted them into a series of instructions coded in a computer language.
\end{itemize}
\end{description}

\vspace{-18.5pt}
\end{document}
