\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin

\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\usepackage{multicol}                % enable multiple columns
\setlength{\columnsep}{18pt}        % increase gap between multicol columns to avoid overlap
\raggedright                         % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% PDF metadata / ATS keywords
\hypersetup{
  pdfauthor={Ryan Heyser},
  pdftitle={Ryan Heyser — Resume},
  pdfkeywords={SRE, Site Reliability Engineering, SLO, SLI, error budget, production readiness review, PRR, incident response, on-call, runbooks, chaos engineering, destructive testing, load testing, Kubernetes, GKE, CRDs, operators, admission webhooks, Gatekeeper, OPA, RBAC, control plane, Wayfinder, Envoy, xDS, GitOps, Flux, HelmRelease, Kustomization, ArgoCD, OpenTelemetry, Prometheus, Grafana, kube-state-metrics, observability, tracing, Vault, OAuth, JWT, OIDC, Workload Identity, cert-manager, Venafi, secrets management, AlloyDB, PostgreSQL, CloudSQL, BigQuery, VPC, Cloud NAT, IAP, IAM, Tailscale, FinOps, Golang, Python, Terraform, Terraform Enterprise, Sentinel, Trivy, Wiz, Chainguard, GCP}
}

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2.5pt, leftmargin=8pt, topsep=6.5pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Ryan Heyser}

\vspace{5pt}

% contact information
\centerline{\href{mailto:ryan.heyser@gmail.com}{ryan.heyser@gmail.com} | \href{https://github.com/ryanheyser}{github.com/ryanheyser}}

\vspace{-18.5pt}

% profile section
\section*{Profile}
\begin{description}
\item\textbf{Site Reliability Engineer and platform leader with 10+ years building, operating, and ensuring the reliability of scalable cloud platforms (GKE, Kubernetes, GCP, Terraform).} Owns reliability quantitatively through SLOs, error budgets, and production-readiness reviews; writes automation and observability tooling in Go and Python that replaces manual runbooks; and translates reliability trade-offs into business outcomes for the 7000+ developers the platform directly supports. Prioritizes platform investment around the majority use case — shipping for the ``80\% customer'' first and solving the long tail as capacity allows. Depth across Kubernetes internals and control-plane management, GitOps delivery, DevSecOps (policy-as-code, secrets management, IaC scanning), and FinOps. \\
\end{description}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\begin{flushleft}
\parbox{\linewidth}{\raggedright
  \textbf{Reliability:} SLO/SLI, error budgets, production-readiness review (PRR), incident response, chaos/destructive \& load testing, PagerDuty\\
  \textbf{Kubernetes:} CRDs, Operators, Admission Webhooks (Gatekeeper/OPA), RBAC, GKE, Wayfinder, Docker, VMware Tanzu\\
  \textbf{Control Plane \& Mesh:} Envoy, xDS, Istio, Linkerd, Tailscale\\
  \textbf{Observability:} OpenTelemetry, Prometheus, Grafana, kube-state-metrics\\
  \textbf{GitOps \& CI/CD:} Flux (HelmReleases, Kustomizations), ArgoCD, GitHub Actions, Jenkins\\
  \textbf{Infrastructure as Code:} Terraform, Terraform Enterprise, Sentinel, Ansible\\
  \textbf{Identity \& Secrets:} Vault, OAuth/JWT/OIDC, Workload Identity, cert-manager, Venafi\\
  \textbf{Cloud \& Networking:} Google Cloud (GKE, GCE, VPC, Cloud NAT, IAP), Azure\\
  \textbf{Databases:} AlloyDB, PostgreSQL, CloudSQL, BigQuery\\
  \textbf{Security:} Sentinel/OPA, Gatekeeper, Trivy, Wiz, Chainguard, IaC scanning\\
  \textbf{Programming Languages:} Golang, Python, Bash\\
  \textbf{AI \& Automation:} Gemini, MCP server\\
  \textbf{Version Control:} Git (Github.com), SVN\\
}
\end{flushleft}

\vspace{-18.5pt}
% projects section
\section*{Projects}
\begin{description}
\item\textbf{Homelab} \hfill \href{https://github.com/ryanheyser/homelab-ops}{github.com/ryanheyser/homelab-ops} | \href{https://github.com/ryanheyser/homelab-infrastructure}{github.com/ryanheyser/homelab-infrastructure} \\
\item\textit{Project to build and maintain homelab through Devops and Infrastructure-as-Code.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item Bootstrap Ubuntu virtual machine image via Cloud Init.
  \item Configure Proxmox VE via Ansible.
  \item Deploy Rancher Kubernetes Engine cluster via Ansible Playbook and configure the cluster to be managed by Fluxcd.
  \item Secrets management via HashiCorp Vault and integration with Kubernetes via External Secrets Operator.
\end{itemize}
\end{description}

\vspace{-18.5pt}

% education section
\section*{Education}
\begin{description}
\item\textbf{Florida Atlantic University} -- MS in Computer Engineering \hfill August 2013
\vspace{-9.5pt}
\item\textbf{Georgia Institute of Technology} -- BS in Computer Engineering \hfill August 2011
\end{description}

\vspace{-18.5pt}

\section*{Experience}
\begin{description}
\item\textbf{Staff Systems Engineer (SRE):} {The Home Depot} -- Atlanta, GA \hfill April 2026 -- Present \\
\textbf{Team:} Site Reliability Engineering \\
\textit{Site Reliability Engineering position owning the reliability of The Home Depot's GKE-based application-delivery platform. Position includes a 24x7 on-call shift. Drive production-readiness reviews (PRR), SLO/error-budget programs, and resiliency testing across the platform; serve as reliability subject-matter expert for platform customers.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Customer Communication:} Served as reliability SME for platform customers — running REASSURE PRR engagements and extending the "Gravity" tool to detect and proactively notify customers of outdated Terraform provider versions.
  \item \textbf{Data:} Operated the platform's managed external data tier (AlloyDB/PostgreSQL) under shared 24x7 on-call — a deliberate, cost-conscious design serving ~80\% of customers with a managed database connection rather than local storage — contributing to production-readiness review, credential hardening, and AlloyDB-to-BigQuery replication reliability.
  \item \textbf{FinOps:} Refactored Google Compute reservation logic for subnet routers and tuned BigQuery dataset billing, reducing recurring spend without degrading capacity or signal.
  \item \textbf{Kubernetes:} Drove lifecycle upgrades of 15+ GKE platform components across 50+ non-production and production clusters — Gatekeeper (OPA admission webhooks), OpenTelemetry and Vault Secrets operators, cert-manager with approver-policy, and kube-rbac-proxy — keeping CRDs, operators, admission control, and RBAC current and continuously scanned (Trivy/Wiz).
  \item \textbf{Kubernetes:} Managed the Envoy/xDS and Appvia Wayfinder control plane and delivered platform components via Flux (HelmReleases and Kustomizations) through a controlled, auditable ``conveyer-belt'' release pipeline, validating routing consistency through rollouts and pod recycles.
  \item \textbf{Networking:} Engineered Tailscale subnet-router and DERP relay networking across GCP VPCs (Cloud NAT, IAP tunnels, Workload Identity) and led destructive failover tests validating regional traffic shifting during incidents.
  \item \textbf{Observability:} Operated the observability stack (OpenTelemetry Collector/Operator, kube-state-metrics, Prometheus, Grafana) across 50+ non-production and production clusters — right-sized alerts at creation and remediated noisy alerts and stale metric descriptors on detection to keep signal high — and streamed audit logs to BigQuery for compliance and forensics.
  \item \textbf{Reliability:} Established the Reliability Engineering practice for the Tailscale platform through the REASSURE production-readiness journey — authored PRRs, defined SLIs/SLOs, and codified destructive-testing plans that surfaced resiliency gaps before customer impact.
  \item \textbf{Reliability:} Defined SLIs/SLOs and a strict production error-budget policy for subnet-router and DERP relay services sustaining 99.999\% availability — zero error-budget breaches since the SRE transition — aligning alerting and on-call response to measurable latency and availability targets.
  \item \textbf{Security:} Hardened the platform identity and secrets tier — Vault (OAuth/JWT/OIDC auth methods), Workload Identity, and cert-manager/Venafi issuance — and built a policy-scoped Vault namespace/path decommission tool gated behind a director-approved change workflow.
  \item \textbf{Strategy:} Shaped platform architecture around the ``80\% customer'' — shipping for the majority of the 7000+ developers the team directly supports first, then solving the remaining long-tail needs as capacity allows.
  \item \textbf{Testing:} Built a reproducible, auditable validation and load-testing harness in Golang and GitHub Actions — reporting latency (p50/p95/p99), service-discovery time, error rate, deployment duration, and time-to-tailnet as deltas against a baseline — and executed destructive and load tests at 3x production scale (~2,000 services across four GCP regions) with node loss, region partition, and rolling pod recycling to validate xDS snapshot consistency and graceful-restart rollout strategies.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Staff Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill March 2024 -- April 2026 \\
\textbf{Team:} Cloud Platform Engineering \\
\textit{Platform Engineering position focused on both software development of platform APIs and platform management. Position includes a 24x7 on-call shift. Provide high-level customer support as the Hashicorp Vault platform subject matter expert. Support Google Cloud Infrastructure via terraform enterprise and sentinel policy-as-code.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Implemented custom DERP servers for cloud-wide Tailscale tailnet communication. Maintain 99.999\% uptime.
  \item \textbf{Application:} Developed Github Actions to automate building of operating system and container images.
  \item \textbf{Deliverability:} Leveraged AI tools (Gemini, MCP server) to automate release notes, test selection, and documentation generation — improving release deliverability and maintaining consistently high deployment success rates.
  \item \textbf{Development:} Built Terraform providers, a node exporter, and cluster smoke-test tooling in Golang to increase automation, observability, and platform reliability.
  \item \textbf{Documentation:} Designed and implemented standardized documentation templating engine via Confluence. Increased documentation creation by the team by over 1000\% the previous two quarters.
  \item \textbf{FinOps:} Led monitoring and metrics cost-optimization that reduced recurring observability spend while preserving signal quality.
  \item \textbf{Incident Management:} Established incident response playbooks, on-call rotation, and blameless postmortems.
  \item \textbf{Leadership:} Owned platform roadmap, prioritized platform investments, and aligned cross-functional stakeholders; led hiring, mentorship, and onboarding programs to accelerate new-hire productivity and retention.
  \item \textbf{Metrics:} Designed and implemented smoke testing infrastructure for Terraform Enterprise implementation. Increased observability of Terraform Enterprise platform and identified cause of systemic deployment issues affecting customers.
  \item \textbf{Reliability:} Defined SLO/SLI program for platform services leading to reduced P99 latency and increased availability.
  \item \textbf{Security:} Integrated policy-as-code (Sentinel/OPA) into Terraform pipelines to enforce guardrails and prevent insecure infrastructure changes.
  \item \textbf{Security:} Hardened the DERP image supply chain — migrated container images to Chainguard, added Trivy scanning to build pipelines, and transitioned certificate issuance from Venafi on-prem to Venafi Cloud.
  \item \textbf{Strategy:} Prioritized platform features around the ``80\% customer'' design philosophy — delivering for the majority of the 7000+ supported developers first and addressing the long tail as capacity allowed.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Staff Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill May 2021 -- March 2024 \\
\textbf{Team:} Developer Operations and Platform Engineering \\
\textit{Platform Engineering position focused on both software development of platform APIs and platform management. Position includes a 24x7 on-call shift. Designed and implemented Kubernetes in the datacenter. Provide high-level customer support as the Kubernetes platform subject matter expert. Provide L4 support for the prior application platform, VMware Tanzu.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Developed a terraform process to create Kubernetes clusters. Process improved Kubernetes customer cluster onboarding down from 2 business weeks to 15 minutes.
  \item \textbf{Application:} Developed terraform providers and APIs to bridge Rancher Kubernetes and Terraform using Golang.
  \item \textbf{Application:} Developed Github Actions to automate building of operating system and container images.
  \item \textbf{Leadership:} Designed and ran team mentorship and people-development programs, and maintained an open-door 1:1 practice to improve shared knowledge and ramp.
  \item \textbf{Metrics:} Designed and implemented metrics and logging infrastructure for Kubernetes to egress metrics and logs from datacenter to Google Cloud.
  \item \textbf{Reliability:} Developed node exporter providing additional metrics of Kubernetes node information in Prometheus format in Golang.
  \item \textbf{Reliability:} Developed node smoke test application to provide real-time cluster status information in Golang.
  \item \textbf{Reliability:} Analyzed metrics usage and was able to reduce recurring cost by half.
  \item \textbf{Security:} Introduced IaC scanning into CI to detect misconfigurations earlier, reducing remediation time and preventing insecure deployments.
  \item \textbf{Strategy:} Applied the ``80\% customer'' design philosophy to the enterprise Kubernetes platform — building for the majority of the internal developer base first and solving edge-case needs as capacity allowed.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Senior Systems Engineer:} {The Home Depot} -- Atlanta, GA \hfill October 2019 -- May 2021 \\
\textbf{Team:} Developer Operations and Platform Engineering \\
\textit{Systems Engineering position focused on both platform management. Position includes a 24x7 on-call shift. Provide high-level customer support. Develop standard template for documentation to improve developer experience with increased ability to document team and external documentation.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Worked to migrate 1000+ applications on VMware Tanzu from CFLINUXFS2 to CFLINUXFS3 over a 3-day period.
  \item \textbf{Documentation:} Created documentation to assist both team standard operating procedure and customers for VMware Tanzu.
  \item \textbf{Reliability:} Maintain supported and secure VMware Tanzu through multiple upgrades.
  \item \textbf{Reliability:} Bring stability to the VMware Tanzu by integrating Min.io, an S3 data backend, significantly reducing customer impact during maintenance windows.
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Verification Engineer:} {Telchemy} -- Duluth, GA \hfill April 2015 -- October 2019 \\
\textit{Designed and implemented automated test tool framework to improve validation of software. Provided high level customer support as an interface between the customer and the development team. Designed and maintained secure lab network providing test framework for 100+ devices and 5000+ virtual devices. Provided manual analysis of reports to validate software stack.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Built, tested, documented and maintained software regression testing tool suite reducing testing cycle from months to weeks.
  \item \textbf{Documentation:} Produce method of procedure maintenance guidelines, produce recommended security practices documentation, for customer integration of products.
  \item \textbf{Reliability:} Designed complex networking configuration for lab testing environment, including network monitoring of all traffic for analysis.
  \item \textbf{Reliability:} Maintain thousands of Linux container instances (LXC, docker) in datacenter.
  \item \textbf{Reliability:} Maintain hundreds of virtual machines (KVM/QEMU, VirtualBox, VMware).
\end{itemize}
\end{description}

\begin{description}
\item\textbf{Airman First Class:} {United States Air Force} -- Boca Raton, FL, Montgomery, AL \hfill October 2012 -- January 2014 \\
\textit{Enrolled in the Technical Degree Sponsorship Program with the US Air Force as an Airman First Class to complete required service.} \\
\vspace{-6.5pt}
\begin{itemize}
  \item \textbf{Application:} Built, tested, and/or modified prototypes using workflow models or theoretical models constructed with computer simulation.
  \item \textbf{Application:} Prepared detailed workflow charts and diagrams that described input, output, and logical operation and converted them into a series of instructions coded in a computer language.
  \item \textbf{Documentation:} Compiled and wrote documentation of program development and subsequent revisions, inserting comments in the coded instructions so others could understand the program.
\end{itemize}
\end{description}

\vspace{-18.5pt}
\end{document}
